---
title: "Bio3d_SA"
author: "Derek Bratcher"
date: "1/3/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Basic intro to PDB strucutre manipulation and analysis with Bio3D

location: http://thegrantlab.org/bio3d_v2/tutorials

```{r}
library(bio3d)
```

list all commands /w `lbio3d()` or 'help(package=bio3d)'.

for help with a function `help(FunctionName)`

use `help.search("topic")` to filter the doccumentation for a specific term
ex 'help.search("pca")'

`example(function)` will execute the listed example of a function from the help file/doccumentation
try `example(plot.bio3d)`

```{r}
example(plot.bio3d)
```


 b-factor values and SS from pdb of 1bg2
 
first read pdb file and map the bfac from pdb coord file to bfac
pdb <- read.pdb( "1bg2" )
bfac <- pdb$atom[pdb$calpha,"b"]

plot bfac and sse (sec struct estimation) add y label and color gray 
plot.bio3d(bfac, sse=pdb, ylab="B-factor", col="gray")

### next plot

use pdb residue numbers and include short sec struct ele


make plot using the bfactors from the pdb file, the sec structure est from applying dssp to pdb, label y axis "b-factor, color is blue, type/typ of plot is line, line width/lwd is 2

plot.bio3d(pdb$atom[pdb$calpha,"b"], sse=sse, ylab="B-factor", typ="l", col="blue", lwd=2)
assign term bfac with bfac col of pdb

next plot

Plot 'aligned' data respecting gap positions /w transducin

read 1tnd from online
pdb = read.pdb("1tnd")

trim pdb for chain a using function atom.select
(when given the pdb and the specified selection based on pdb it returns the atom n xyz coordinates)

 pdb = trim.pdb(pdb, inds=atom.select(pdb, chain="A"))
 
 plot b factor values with gaps
 
 make a plot of the bfactors col of pdb vs pdb residues, add sec struct ele based on dssp of pdb. label y axis b-factor

plot.bio3d(pdbs$b, resno=pdb, sse=pdb, ylab="B-factor")

 Plot of B-factor values after removing all gaps

plot.bio3d(pdbs$b, rm.gaps=TRUE, resno = pdb, sse=pdb, ylab="B-factor")

detatch transducin to remove from search path
detach(transducin)

also r can always be interrupted /w ctrl+c
q() to quit the current session
run `demo(package="bio3d")` to see what else bio3d can do
run `demo("nma")` on specific functions like nma to specify the demo

Remember that you can get help on any particular function by using the command `?function` or `help(function)` from within R. 

You can save an external representation of any R objects to a specified file using the save()command.  The objects can be read back from the file at a later time by using the function `load()`.




```{r}
# Plot of B-factor values along with secondary structure from PDB

plot.bio3d(pdb$atom[pdb$calpha,"b"], sse=pdb, resno=pdb, ylab="B-factor", typ="l", lwd=1.5, col="blue", sse.min.length=0)
```

```{r}
# Calculate secondary structure using stride() or dssp()

sse_d <- dssp(pdb, exefile = '/usr/local/bin/mkdssp')

# Plot of B-factor values along with calculated secondary structure

plot.bio3d(pdb$atom[pdb$calpha,"b"], sse=sse_d, ylab="B-factor", typ="l", col="blue", lwd=2)

```


```{r}
# Plot 'aligned' data respecting gap positions

attach(transducin)
pdb_b = read.pdb("1tnd")

pdb_b = trim.pdb(pdb_b, inds=atom.select(pdb_b, chain="A"))

# Plot of B-factor values with gaps

plot.bio3d(pdbs$b, resno=pdb_b, sse=pdb_b, ylab="B-factor")
```
# bio3d style

bio3d is mainly composed of input output functions that convert alter analyze or graph data. the write up is available via `help(package=bio3d)` or by the commands like `help.search("topic/function")` or "http://thegrantlab.org/bio3d_v2/html/index.html"
run `example(function)` to give an example as per the function. tuitorials on more complicated jobs are here "http://thegrantlab.org/bio3d_v2/tutorials"

## Reading a PDB

the `read pdb()` function can read a previously saved pdb file from local storage or pull from online pdb repository if given RCSB PBD ID

```{r}
#save pdb of protooncogenic ras protein 4q21 as pdb_1
pdb_1<- read.pdb("4q21")

# use print(pdb_1) or just pdb_1 to call a quick summary of 4q21 and view(pdb_1) to open separate page

print(pdb_1)

#notice the other values/attributes abbreviated at bottom 
attributes(pdb_1)
#treat like columns of a dataset and call via pdb_1$attribute
head(pdb_1$calpha)
#print data of first two atoms
pdb_1$atom[1:2, ]
# print a subset of the first two atoms based on atom serial number and atom type and space coordinates
pdb$atom[1:2, c("eleno", "elety", "x","y","z")]



```

using `plot.bio3d` with subsetting of the values/elements/attributes i can assemble a graph based on bfactors  of residues of 4q21 and use sse to apply est sec structure approx to top and btm 

```{r}
plot.bio3d(pdb$atom$b[pdb$calpha], sse=pdb, typ="l", ylab="B-factor")
```

objects created by `read.pdb()` are written to be of class pdb this tells other generic functions (like `atom.select(), nma(), print(), summary()` ect) how to proccess present the result of such data. 
the pdb output is also given a second class (sse secondary structure elements) such that functions like `plot.bio3d` make use of the estimated sec structs and apply to the plot based on the residues involved
