---
title: "Cloning R_projs"
author: "DerekRBratcher"
date: "12/21/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Cloning repos /w R

When you want to pull a repo from git hub to work on its as simple as copying the code on github
+ through github find the repo with the info you want
+ Now click the big green button that says “<> Code” (copy the HTTPS URL)

1st https://github.com/Deebee33/aftr_7800
2nd click code and copy the https url (the location of the code on github to direct your terminal)
closing your current project such that you have a uncomitted workspace

switching wd to your github dir for organization
```{r, eval=FALSE}
#in the WSL terminal, starting from home dir (absolute path(/home/derek)), relative path(~/)
cd ~/Documents/GitHub or cd /home/derek/Documents/GitHub

# then clone /w git clone (paste https url)
git clone https://github.com/Deebee33/aftr_7800.git


```

then using the WSL terminal to clone the https address of the code you want to work on
