---
title: "Cloning R_projs"
author: "DerekRBratcher"
date: "12/21/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Cloning repos /w R
https://happygitwithr.com/push-pull-github.html

When you want to pull a repo from git hub to work on its as simple as copying the code on github
+ through github find the repo with the info you want
+ Now click the big green button that says “<> Code” (copy the HTTPS URL)

1st https://github.com/Deebee33/aftr_7800
2nd click code and copy the https url (the location of the code on github to direct your terminal)
closing your current project such that you have a uncommitted workspace

switching wd to your github dir for organization
```{r, eval=FALSE}
#in the WSL terminal, starting from home dir (absolute path(/home/derek)), relative path(~/)
cd ~/Documents/GitHub or cd /home/derek/Documents/GitHub

# then clone /w git clone (paste https url)
git clone https://github.com/Deebee33/aftr_7800.git


```

then using the WSL terminal to clone the https address of the code you want to work on

Make this new repo your working directory, list its files, display the README, and get some information on its connection to GitHub:

`cd myrepo`
`ls`
`head README.md`
`git remote show origin`

Make a local change, commit, and push
Add a line to README and verify that Git notices the change:

`echo "A line I wrote on my local computer  " >> README.md`
`git status`

derek@red:~/Documents/GitHub/aftr_7800$ git remote show origin
* remote origin
  Fetch URL: https://github.com/Deebee33/aftr_7800.git
  Push  URL: https://github.com/Deebee33/aftr_7800.git
  HEAD branch: main
  Remote branch:
    main tracked
  Local branch configured for 'git pull':
    main merges with remote main
  Local ref configured for 'git push':
    main pushes to main (up to date)
derek@red:~/Documents/GitHub/aftr_7800$ echo "writing this from the red remote at B&N" >> README.md
derek@red:~/Documents/GitHub/aftr_7800$ git status
On branch main
Your branch is up to date with 'origin/main'.

Changes not staged for commit:
  (use "git add <file>..." to update what will be committed)
  (use "git restore <file>..." to discard changes in working directory)
        modified:   README.md

no changes added to commit (use "git add" and/or "git commit -a")
derek@red:~/Documents/GitHub/aftr_7800$ git add <README.md>
bash: syntax error near unexpected token `newline'
derek@red:~/Documents/GitHub/aftr_7800$ git add README.md
derek@red:~/Documents/GitHub/aftr_7800$ git commit README.md

 Please enter the commit message for your changes. Lines starting
# with '#' will be ignored, and an empty message aborts the commit.
# On branch master
this is VIM editor change to doom emacs
 In vim, you can press i to start entering text and save by pressing esc and :wq which would commit the message you entered.

In the above state, to quit without committing, you can do :q instead of the :wq as mentioned above.


This is a text editor, likely vi or vim.

You can press the i key to go insert mode and type your commit message, escape when you're done, then ZZ (twice, uppercase) to exit.

Or, you can put the commit message in the command line with the -m option.

The text editor has some nice perks, like being able to easily enter new lines, etc. If vi isn't good for you, you can use git config --global core.editor <editorname> to change your editor to something more to your liking.
https://stackoverflow.com/questions/39798997/how-do-i-complete-a-git-commit

[main 0fdb4ca] an update from B&N
 1 file changed, 1 insertion(+)
